Unsupervised embeddings of organizations capture the latent structure of scientific mobility

### 2020-06-10 paper/current/main.tex
update figure caption, sentence -> trajectory

%
% Figure - Example of mobility sentences
%
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{\figdir/mobility_example_combined.pdf}
    \caption{
        \textbf{Co-affiliation trajectories represented as sentences}
        \textbf{a.}
        An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence ordered by year of publication.
        \textbf{b.}
        In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials). 
    }
    \label{fig:methods:mobility_sentence}
\end{figure}

>>>>

%
% Figure - Example of mobility sentences
%
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{\figdir/mobility_example_combined.pdf}
    \caption{
        \textbf{Construction of mobility trajectories from publication records}
        \textbf{a.}
        An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
        To each organization, a unique identifier is assigned, and they are assembled into a mobility trajectory ordered by year of publication.
        \textbf{b.}
        In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials). 
    }
    \label{fig:methods:mobility_sentence}
\end{figure}
